Simulation Figures for Genome Biology (simulations)

### 2018-07-09 manuscript_figures/manuscript_figures_sims.Rmd
Fix info, pi0 sim plots and clean up into single figure

```{r}
res_pi0set <- dplyr::filter(res, grepl("varyingpi0", setting))
res_pi0set <- dplyr::rename(res_pi0set, pi0 = dist)
res_pi0set <- dplyr::mutate(res_pi0set, pi0 = as.numeric(gsub("nullprop", "", pi0)))
res_pi0set <- tidyr::complete(res_pi0set, setting, Method, pi0, key)
res_pi0set <- dplyr::mutate(res_pi0set, setting = factor(setting, levels = c("varyingpi0", "varyingpi0-lowsignal"),
                                                         labels = c("high signal", "low signal")))
```

## including SE to show variability in FDRR
pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "FDR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Mean FDR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

## including SE to show variability in FDRR
ptpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Mean TPR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))
```

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(pfdr + guides(color = FALSE, linetype = FALSE),
                ptpr, rel_widths = c(1, 1.25), labels = LETTERS[1:2])
gp

ggsave(file.path(outdir, "FigureSsim-nullprop.pdf"), gp, width = 10, height = 5)

## trimmed ranges
gp_zoom <- plot_grid(pfdr + coord_cartesian(ylim = c(0, .25)) + guides(color = FALSE, linetype = FALSE),
                     ptpr, rel_widths = c(1, 1.25), labels = LETTERS[1:2])
gp_zoom

ggsave(file.path(outdir, "FigureSsim-nullprop-zoom.pdf"), gp_zoom, width = 10, height = 5)
```

@@

@@

```{r}
res_infoset <- dplyr::filter(res, grepl("varyinginfo", setting))
res_infoset <- dplyr::rename(res_infoset, level = dist)
res_infoset <- dplyr::mutate(res_infoset, level = as.numeric(gsub("level", "", level)))
res_infoset <- tidyr::complete(res_infoset, setting, Method, level, key)
res_infoset <- dplyr::mutate(res_infoset, setting = factor(setting, levels = c("varyinginfo", "varyinginfo-lowsignal"),
                                                         labels = c("high signal", "low signal")))
```

@@

## including SE to show variability in FDRR
pfdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "FDR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Mean FDR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

## not including SE because it's too small
pfdr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, se, q10, q90, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    facet_grid(setting ~ .) + 
    ggtitle("Mean FDR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))
pfdr

ptpr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    facet_grid(setting ~ ., scales = "free_y") + expand_limits(y = 0) +
    ggtitle("Mean TPR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))
ptpr
```

@@

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(pfdr + guides(color = FALSE, linetype = FALSE), ptpr,
          rel_widths = c(1, 1.25), labels = LETTERS[3:4])
gp

@@

>>>>

@@

```{r}
res_pi0set <- dplyr::filter(res, setting == "varyingpi0-lowsignal")
res_pi0set <- dplyr::rename(res_pi0set, pi0 = dist)
res_pi0set <- dplyr::mutate(res_pi0set, pi0 = as.numeric(gsub("nullprop", "", pi0)))
res_pi0set <- tidyr::complete(res_pi0set, setting, Method, pi0, key)
```

## including SE to show variability in FDRR
pi0_fdr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "FDR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    ggtitle("Mean FDR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

## including SE to show variability in FDRR
pi0_tpr <- dplyr::select(res_pi0set, Method, setting, pi0, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR", !is.na(mean_value)) %>%
    ggplot(aes(x = pi0 / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Null Proportion", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    ##facet_grid(setting ~ .) + 
    ggtitle("Mean TPR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))
```

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(pi0_fdr + guides(color = FALSE, linetype = FALSE),
                pi0_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2])
gp <- plot_grid(gp, get_legend(pi0_tpr), rel_widths = c(1, .125))
gp

ggsave(file.path(outdir, "FigureSsim-nullprop.pdf"), gp, width = 10, height = 5)
```

@@

```{r}
res_infoset <- dplyr::filter(res, setting == "varyinginfo-lowsignal")
res_infoset <- dplyr::rename(res_infoset, level = dist)
res_infoset <- dplyr::mutate(res_infoset, level = as.numeric(gsub("level", "", level)))
res_infoset <- tidyr::complete(res_infoset, setting, Method, level, key)
```

@@

## not including SE because it's too small
info_fdr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, se, q10, q90, col, lty) %>%
    dplyr::filter(key == "FDR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    geom_hline(yintercept = 0.10, color = "red", lty = 2, alpha = 1/3) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("FDR", labels = scales::percent) + 
    ggtitle("Mean FDR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))

info_tpr <- dplyr::select(res_infoset, Method, setting, level, key, mean_value, se, col, lty) %>%
    dplyr::filter(key == "TPR") %>%
    ggplot(aes(x = level / 100, y = mean_value, color = Method, lty = Method)) +
    geom_line(alpha = 0.85, position = position_dodge(width = .01)) +
    geom_errorbar(aes(ymin = mean_value - se, ymax = mean_value + se), width=0.025, alpha=0.5) +
    scale_color_manual(values = col) +
    scale_linetype_manual(values = lty) + 
    scale_x_continuous("Informativeness", labels = scales::percent, breaks = seq(0, 1, .1)) + 
    scale_y_continuous("TPR", labels = scales::percent) + 
    expand_limits(y = 0) +
    ggtitle("Mean TPR Over 100 Replications") +
    theme_classic() +
    theme(axis.title = element_text(face="bold", size = 10),
          plot.title = element_text(face="bold", size = 14))
```

@@

```{r, fig.width = 15, fig.height = 7.5}
gp <- plot_grid(info_fdr + guides(color = FALSE, linetype = FALSE),
                info_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2])
gp <- plot_grid(gp, get_legend(info_tpr), rel_widths = c(1, .125))
gp

@@

We also create a single plot with simulation results for both varying pi0 and varying
informativeness settings.

```{r}
gp <- plot_grid(pi0_fdr + guides(color = FALSE, linetype = FALSE),
                pi0_tpr + guides(color = FALSE, linetype = FALSE),
                info_fdr + guides(color = FALSE, linetype = FALSE),
                info_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:4])
gp <- plot_grid(gp, get_legend(info_tpr), rel_widths = c(1, .2))
gp

ggsave(file.path(outdir, "FigureAlt-Sims.pdf"), gp, width = 10, height = 8)
```
